Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores. II. Nanoflare Trains

### 2016-10-14 tex/paper.tex
first draft after first round of referee feedback

	\par The concept of heating the solar corona by nanoflares, first proposed by \citet{parker_nanoflares_1988}, has been developed extensively over the past two decades \citep[e.g.][]{cargill_implications_1994,cargill_nanoflare_2004,klimchuk_solving_2006}. The term \textit{nanoflare} has now become synonomous with impulsive heating in the energy range $10^{24}-10^{27}$ erg, with no specific assumption regarding the underlying physical mechanism (for example, small-scale magnetic reconnection or hydromagnetic wave dissipation). In active region (AR) cores such as those we discuss in this paper, one strategy for constraining potential heating models is the analysis of the emission measure distribution as a function of temperature, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$. \citet{cargill_implications_1994,cargill_nanoflare_2004} predicted that $\mathrm{EM}(T)$ resulting from nanoflare heating should be wide, with a maximum value at $T=T_m\sim10^{6.5}$ K and have a faint, high-temperature (8-10 MK) component. Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}. Observations from instruments onboard the \textit{Solar Dynamics Observatory} \citep[\textit{SDO},][]{pesnell_solar_2012} and \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{tripathi_emission_2011,warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,schmelz_cold_2012,del_zanna_evolution_2015}.

@@

	\par The loop is heated by a prescribed heating function, applied to either the electrons ($\bar{Q}_e$) or the ions ($\bar{Q}_i$). Both species cool through a combination of thermal conduction ($F_{ce,0},\,F_{ci,0}$) and an enthalpy flux to the lower atmosphere, with the electrons also undergoing radiative cooling ($\mathcal{R_C}$). In the case of conductive cooling, a flux limiter, $F_s=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma. In all cases we use a saturation limit of $f=1$. See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the heating rate for each event is $H_i=H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg.

@@

		\caption{Emission measure distributions for waiting times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the waiting time after each event is proportional to the heating rate of the event (green). For the last case ($\beta=1$), $t_N$ is the average waiting time for all events. Note that in some panels, the blue $\beta=0$ curves may not be visible because they overlap heavily with the green $\beta=1$ curves. The solid lines in the two power law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution. The standard deviation is not included in the NEI results.}

@@

	\par In \autoref{subsec:heating_stats}, we noted that for heating functions using a power-law energy distribution, for each $t_N$, we run the model $N_R$ times. Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves. In order to present our results compactly, the solid lines in \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the mean $\mathrm{EM}(T)$ over all $N_R$ curves. The shading represents $1\sigma$ from the mean. In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the power-law distribution of possible heating rates.

@@

	\authorcomment1{TODO:Change/update all temperatures ratio references appropriately. TODO: add additional figure/paragraph describing how changes in hot/cool temperatures are likely to affect our result}

@@

		\plottwo{../results/ratio_hist_alpha_single_T1.pdf}{../results/ratio_hist_twait_single_T1.pdf}
		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, for all heating function types and heating frequencies for the single fluid case. In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citet{scargle_studies_2013} as implemented in the astroML Python package for statistical learning in astronomy \citep{vanderplas_introduction_2012}. \textbf{Left:} Emission measure ratios separated by heating function type for all heating frequencies, $250\le t_N\le5000$ s. Because there are too few ($<20$) $\mathrm{EM}$ ratio measurements for the uniform case to construct a meaningful histogram, we denote the median of the uniform results with a vertical line, shown here in purple. \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$. For aesthetic purposes, only five values of $t_N$ are shown, $t_N=1000,2000,3000,4000,5000$ s.}

@@

		\plottwo{../results/ratio_hist_alpha_electron_T1.pdf}{../results/ratio_hist_twait_electron_T1.pdf}

@@

		\plottwo{../results/ratio_hist_alpha_ion_T1.pdf}{../results/ratio_hist_twait_ion_T1.pdf}

@@

	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and \textbf{for this paper consider $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, the formation temperatures of Fe XIX and XII, respectively \citep[i.e. the temperature $T$ which maximizes the contribution function $G_{\lambda}(T)$ calculated using CHIANTI v8,][]{dere_chianti_1997,del_zanna_chianti_2015}}. This also provides a way to compare in a concise way every point in our multidimensional parameter space though we acknowledge that we are reducing $8\times10^4$ s of loop evolution to a single value. This ratio is shown in \autoref{fig:em_ratio_hist_single}, \autoref{fig:em_ratio_hist_el}, and \autoref{fig:em_ratio_hist_ion} for the single-fluid model, electron and ion heating, respectively. In the left-hand panels each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e. $\beta=0$). The right panels show these same emission measure ratios, but now categorized by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.

	\par Considering first the left hand panels, in the single fluid model (\autoref{fig:em_ratio_hist_single}) the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$). Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}. For electron heating (\autoref{fig:em_ratio_hist_el}) the ratio is again insensitive to $\alpha$, but is narrower and falls off more quickly toward higher emission measure ratios. The $\beta=0$ cases (for all $\alpha$) peak near $0.5$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1. For ion heating (\autoref{fig:em_ratio_hist_ion}) the $\beta=0$ distributions peak at lower values compared to those with $\beta=1$. Again the results are relatively insensitive to $\alpha$. However, compared to the electron heating case, all of the distributions are much wider and peak at higher values, $\sim1.5$ for $\beta=0$ and $>2$ for $\beta=1$. Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.

	\par Turning to the right hand panels, in the single-fluid model for $t_N\le4000$ s, the results cluster just near 1.0, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.25$. Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim1.5$ and does not ``pile up'' near 1.0 as the other values of $t_N$ do. For electron heating, the $t_N=3000$ s distribution has a very strong and narrow peak at $\sim0.5$ while all of the other distributions peak at $\sim1$. For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s. Finally, for ion heating the distributions for each value of $t_N$ are much wider than for the single fluid and electron heating cases and the peak values show a stronger dependence on $t_N$. The range of peak values is also much larger, with the $t_N=1000$ s case peaking near 0 and the $t_N=5000$ s case peaking just above $2$. As in \autoref{fig:em_ratio_hist_single}, we see that the $t_N=3000$ s distribution is bimodal. In general, the distributions grouped by $t_N$ for all three heating types have a positive skew and are peaked in the range $\sim0.5-1.5$ except for some extreme cases in the ion heating scenario.

@@

	\par These results suggest that the emission measure ratio is generally in the range $\sim0.5-1.5$, with some higher values. Given the uncertainties in the atomic physics, This seems to support the conclusion of the presence of nanoflare heating by \citet{brosius_pervasive_2014}. Thus the calculation of such ratios from limited data has the potential to be a powerful diagnostic of the existence of nanoflare heating. Whether one can say more about the precise form of nanoflare heating is less clear. In these results the ratios are largely independent of the power-law index $\alpha$ and only weakly-dependent on the waiting time, $t_N$. Furthermore, the distributions are also weakly dependent on the relationship between the waiting time and heating rate, $\beta$. The exception is the ion heating case where the distributions are much wider, peak at higher values, and show a stronger dependence on $\alpha$, $\beta$, and $t_N$. The problem with drawing conclusions from the details of these results lies in the numerous uncertainties in any data, especially concerning atomic physics.

@@

	\par Two possible ways to relate these results to present and future observations were discussed. First we showed that while below $T_m$ the well-known relation $\mathrm{EM}\sim T^a$ was quite robust, that was not the case above $T_m$. On the other hand the calculation of a ratio between the emission measure at a pair of temperatures above and below $T_m$ held more promise. For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}=10^{6.95}>T_m$ and $T_{cool}=10^{6.2}<T_m$, was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors. Further observational evidence of such ratios would, in our view, provide a very strong case for the presence of nanoflare heating. On the other hand, given the uncertainties in atomic physics and emission emasure analysis, such a comparison seems unlikely to be able to shed more detailed light on the details (e.g. $t_N$, $\alpha$, $\beta$) of the actual heating process.

@@

	\software{astroML \citep{vanderplas_introduction_2012}, IPython/Jupyter \citep{perez_ipython:_2007}, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, scipy \citep{van_der_walt_numpy_2011}}

>>>>

	\par The concept of heating the solar corona by nanoflares, first proposed by \citet{parker_nanoflares_1988}, has been developed extensively over the past two decades \citep[e.g.][]{cargill_implications_1994,cargill_nanoflare_2004,klimchuk_solving_2006}. The term \textit{nanoflare} has now become synonomous with impulsive heating in the energy range $10^{24}-10^{27}$ erg, with no specific assumption regarding the underlying physical mechanism (for example, small-scale magnetic reconnection or hydromagnetic wave dissipation). In active region (AR) cores such as those we discuss in this paper, one strategy for constraining potential heating models is the analysis of the emission measure distribution as a function of temperature, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$. \citet{cargill_implications_1994,cargill_nanoflare_2004} predicted that the $\mathrm{EM}(T)$ resulting from nanoflare heating should be wide, with a maximum value at $T=T_m\sim10^{6.5}$ K and have a faint, high-temperature (8-10 MK) component. Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}. Observations from instruments onboard the \textit{Solar Dynamics Observatory} \citep[\textit{SDO},][]{pesnell_solar_2012} and \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{tripathi_emission_2011,warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,schmelz_cold_2012,del_zanna_evolution_2015}.

@@

	\par The loop is heated by a prescribed heating function, applied to either the electrons ($\bar{Q}_e$) or the ions ($\bar{Q}_i$). Both species cool through a combination of thermal conduction ($F_{ce,0},\,F_{ci,0}$) and an enthalpy flux to the lower atmosphere, with the electrons also undergoing radiative cooling ($\mathcal{R_C}$). In the case of conductive cooling, a flux limiter, $F_s=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma. In all cases we use a saturation limit of $f=1$. See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to affect the presence of hot emission in a nanoflare-heated plasma.

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the heating rate for each event is $H_i=H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm and cross-sectional area $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg.

@@

		\caption{Emission measure distributions for waiting times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the waiting time after each event is proportional to the heating rate of the event (green). For the last case ($\beta=1$), $t_N$ is the average waiting time for all events. Note that in some panels, the blue $\beta=0$ curves may not be visible because they overlap heavily with the green $\beta=1$ curves. The solid lines in the two power law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates one standard deviation from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution. The standard deviation is not included in the NEI results.}

@@

	\par In \autoref{subsec:heating_stats}, we noted that for heating functions using a power-law energy distribution, for each $t_N$, we run the model $N_R$ times. Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves. In order to present our results compactly, the solid lines in \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the mean $\mathrm{EM}(T)$ over all $N_R$ curves. The shading represents one standard deviation from the mean. In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the power-law distribution of possible heating rates.

@@

@@

		\plottwo{../results/ratio_hist_alpha_single_T0.pdf}{../results/ratio_hist_twait_single_T0.pdf}
		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, for all heating function types and heating frequencies for the single fluid case. In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citet{scargle_studies_2013}. \textbf{Left:} Emission measure ratios separated by heating function type for all heating frequencies, $250\le t_N\le5000$ s. Because there are too few ($<20$) $\mathrm{EM}$ ratio measurements for the uniform case to construct a meaningful histogram, we denote the median of the uniform results with a vertical line, shown here in purple. \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$. For aesthetic purposes, only five values of $t_N$ are shown, $t_N=1000,2000,3000,4000,5000$ s.}

@@

		\plottwo{../results/ratio_hist_alpha_electron_T0.pdf}{../results/ratio_hist_twait_electron_T0.pdf}

@@

		\plottwo{../results/ratio_hist_alpha_ion_T0.pdf}{../results/ratio_hist_twait_ion_T0.pdf}

@@

	\par We define a general emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$ and \textbf{for this paper consider $T_{hot}=10^{6.942}$ K and $T_{cool}=10^{6.187}$ K, the formation temperatures of Fe XIX and XII, respectively \citep[i.e. the temperature $T$ which maximizes the contribution function $G_{\lambda}(T)$ calculated using CHIANTI v8,][]{dere_chianti_1997,del_zanna_chianti_2015}}. This also provides a way to compare in a concise way every point in our multidimensional parameter space though we acknowledge that we are reducing $8\times10^4$ s of loop evolution to a single value. This ratio is shown in \autoref{fig:em_ratio_hist_single}, \autoref{fig:em_ratio_hist_el}, and \autoref{fig:em_ratio_hist_ion} for the single-fluid model, electron and ion heating, respectively. In the left-hand panels each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are evenly spaced (i.e. $\beta=0$) and chosen from a power-law distribution of $\alpha=-1.5$. The right panels show these same emission measure ratios, but now categorized by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes.

	\par Considering first the left hand panels, in the single fluid model (\autoref{fig:em_ratio_hist_single}) the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim1-1.25$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.5$). Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.6$) show emission measure ratios significantly less than those in the power law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}. For electron heating (\autoref{fig:em_ratio_hist_el}) the ratio is again insensitive to $\alpha$, but is narrower and falls off more quickly toward higher emission measure ratios. The $\beta=0$ cases (for all $\alpha$) peak just above $0.5$, with the $\beta=1$ cases all peaking at slightly higher values just at or below 1. For ion heating (\autoref{fig:em_ratio_hist_ion}) the $\beta=0$ distributions peak at lower values compared to those with $\beta=1$. Again the results are relatively insensitive to $\alpha$. However, compared to the electron heating case, all of the distributions are much wider and peak at higher values, $\sim1.75$ for $\beta=0$ and $\sim2-2.5$ for $\beta=1$. Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.

	\par Turning to the right hand panels, in the single-fluid model for $t_N\le4000$ s, the results cluster just near 1.5, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.5$. Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim2$ and does not ``pile up'' near $1.5$ as the other values of $t_N$ do. For electron heating, the $t_N=3000$ s distribution has a very strong and narrow peak at $\sim0.5$ while all of the other distributions peak at $\sim1-1.5$. For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s. Finally, for ion heating the distributions for each value of $t_N$ are much wider than for the single fluid and electron heating cases and the peak values show a stronger dependence on $t_N$. The range of peak values is also much larger, with the $t_N=1000$ s case peaking near 0 and the $t_N=5000$ s case peaking just at $\sim2.5$. As in \autoref{fig:em_ratio_hist_single}, we see that the $t_N=3000$ s distribution is bimodal. In general, the distributions grouped by $t_N$ for all three heating types have a positive skew and are peaked in the range $\sim0.5-2$ except for some extreme cases in the ion heating scenario.

@@

	\par These results suggest that the emission measure ratio is generally in the range $\sim0.5-2$, with some higher values. Given the uncertainties in the atomic physics, this seems to support the conclusion of the presence of nanoflare heating by \citet{brosius_pervasive_2014}. Thus the calculation of such ratios from limited data has the potential to be a powerful diagnostic of the existence of nanoflare heating. Whether one can say more about the precise form of nanoflare heating is less clear. In these results the ratios are largely independent of the power-law index $\alpha$ and only weakly-dependent on the waiting time, $t_N$. Furthermore, the distributions are also weakly dependent on the relationship between the waiting time and heating rate, $\beta$. The exception is the ion heating case where the distributions are much wider, peak at higher values, and show a stronger dependence on $\alpha$, $\beta$, and $t_N$. The problem with drawing conclusions from the details of these results lies in the numerous uncertainties in any data, especially concerning atomic physics.
	\subsubsection{Additional Line Pairs}
	\label{subsubsec:add_line_pairs}
		\plotone{../results/em_ratio_versus_tn.pdf}
		\caption{Emission measure ratio as a function of $t_N$ for the single-fluid (left), electron heating (center), and ion heating (right) cases for four different line pairs: Fe XIX/Fe XII (blue), Fe XIX/Fe XV (green), Fe XX/Fe XII (red), and Fe XX/Fe XV (yellow). The formation temperatures of Fe XV and Fe XX, calculated using CHIANTI v8, are $10^{6.342}$ K and $10^{7.027}$ K, respectively. The circles ($\beta=0$) and stars ($\beta=1$) indicate the mean EM ratio calculated over all runs for a given $t_N$ (see \autoref{subsec:heating_stats}) and the error bars indicate one standard deviation from the mean.}
		\label{fig:em_ratio_vs_tn}
	\par \textbf{Because our proposed EM ratio diagnostic is based on only two points from each $\mathrm{EM}(T)$, it is reasonable to ask how this measurement might be affected by a different choice of hot/cool temperatures. \autoref{fig:em_ratio_vs_tn} shows the mean EM ratio (with the error bars corresponding to one standard deviation) as a function of $t_N$ for three additional line pairs: Fe XIX/XV, Fe XX/XII, and Fe XX/XV, as denoted by the color coding. The circles (stars) correspond to $\beta=0(1)$ and we consider only $\alpha=-2.5$ here. The values of the line ratios can be organized from high to low as Fe XIX/Fe XII, Fe XX/Fe XII, Fe XIX/Fe XV and Fe XX/Fe XV. The second and third pairs have similar ratio values. This ordering is to be expected from the general shape of the $\mathrm{EM}(T)$ curves, although the exact ratios cannot be predicted in any simple way.}
	\par \textbf{For $\beta=1$, the ratio decreases monotonically as $t_N$ decreases, however the values of the ratio lie within a narrow band. Given the many uncertainties in the measurements, it is unlikely that any of these line pairs can provide an unequivocal constraint on $t_N$. For $\beta=0$, there is an upturn in the ratio between $t_n = 2000$ s and $3000$ s, and below this value, the ratios are ill-defined due to lack of plasma at one or both of the measured temperatures. At lower temperatures, this arises because, for an evenly spaced nanoflare train, there is a sharp cut-off in $\mathrm{EM}(T)$ at some temperature $T< T_m$ which does not occur when a waiting time is included \citep{cargill_active_2014}.} 
	\par \textbf{On the other hand, the relative ratios of line pairs is a quantitative prediction that can be examined were such data to be available, and can be easily extended to other line pairs not considered here. In addition, for all line pairs, the detection of an emission measure ratio lying between the upper and lower bounds shown can be regarded as a very strong indicator of the presence of ``hot'' nanoflare-produced plasma. Further deductions require more detailed modeling of in particular the atomic physics which is beyond the scope of this paper.}

@@

	\par Two possible ways to relate these results to present and future observations were discussed. First we showed that while below $T_m$ the well-known relation $\mathrm{EM}\sim T^a$ was quite robust, that was not the case above $T_m$. On the other hand the calculation of a ratio between the emission measure at a pair of temperatures above and below $T_m$ held more promise. For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}=10^{6.942}>T_m$ and $T_{cool}=10^{6.187}<T_m$, was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors. Further observational evidence of such ratios would, in our view, provide a very strong case for the presence of nanoflare heating. On the other hand, given the uncertainties in atomic physics and emission emasure analysis, such a comparison seems unlikely to be able to shed more detailed light on the details (e.g. $t_N$, $\alpha$, $\beta$) of the actual heating process.

@@

	\software{astroML \citep{vanderplas_introduction_2012}, IPython/Jupyter \citep{perez_ipython:_2007}, matplotlib \citep{hunter_matplotlib:_2007}, NumPy/scipy \citep{van_der_walt_numpy_2011}, seaborn \citep{waskom_seaborn:_2016}}
